\begin{frame}
  \frametitle{Publications}
  \framesubtitle{Published}

  \monocolumn{
    \begin{itemize}
      \compresslist
    \item \mhsII
      \begin{itemize}
        \tiny
      \item \textbf{Cardoso, N. and Abreu, R. 2014. An efficient
          distributed algorithm for computing minimal hitting sets.
          In Proceedings of the 25$^\text{th}$ International Workshop
          on Principles of Diagnosis, DX’14. (Best Paper Award) }
      \item Cardoso, N. and Abreu, R. 2013. \mhsII: A map-reduce
        heuristic-driven minimal hitting set search algorithm. In
        Proceedings of the 2013 International Conference on Multicore
        Software Engineering, Performance, and Tools, MUSEPAT’13,
        pages 25–36.
      \item Cardoso, N. and Abreu, R. 2013. A distributed approach
        to diagnosis candidate generation. In Proceedings of the 16$^\text{th}$ Portuguese
        Conference on Artificial Intelligence, EPIA’13, pages 175–186.
      \end{itemize}

    \item Fuzzinel
      \begin{itemize}
        \tiny
      \item \textbf{Cardoso, N. and Abreu, R. 2014. Enhancing
          reasoning approaches to diagnose functional and
          non-functional errors. In Proceedings of the 25$^\text{th}$
          International Workshop on Principles of Diagnosis,
          DX’14. (Best Paper Award Nominee) }
      \end{itemize}

    \item NFGE
      \begin{itemize}
        \tiny

      \item \textbf{Cardoso, N. and Abreu, R. 2013. A kernel density
          estimate-based approach to component goodness modeling. In
          Proceedings of the 27$^\text{th}$ AAAI Conference on
          Artificial Intelligence, AAAI’13.}
      \end{itemize}
    \end{itemize}
  }

\end{frame}
